Misperceived Social Norms about Women Working Outside the Home and Its Effect on Women in Saudi Arabia

### 2024-02-12 outputs/paper/paper.qmd
include abstract

---
title: "Misperceived Social Norms about Women Working Outside the Home and Its Effect on Women in Saudi Arabia"
author: 
  - Boxuan Yi
  - Ruoxian Wu
thanks: "Code and data are available at: https://github.com/ScarletWu/Misperceived-Social-Norms-Women-Working-Outside-the-Home-in-Saudi-Arabia. Replication on Social Science Reproduction platform available at: https://www.socialsciencereproduction.org/reproductions/1557/"
date: "February 12, 2024"
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

Our paper will follow a reproduction of Leonardo Bursztyn, Alessandra L. González, and David Yanagizawa-Drott’s findings. We seek to replicate two claims, (1) There is a wedge between the actual and perceived proportion of men supporting women working outside the home, and (2) Most Saudi men who privately support WWOH fail to understand that others do as well, and they are more likely to help their wives find jobs when they know the actual portion of men supporting WWOH. The experiments and surveys results we will try to replicate are (1) the actual portion of support of WWOH from young husbands, (2) the existence of misperception, and (3) the effects of correcting beliefs on wives in Saudi Arabia. Our reproduction used the programming language R [@r], the analysis used the following packages: Haven[@rHaven], Dplyr [@rDplyr], Ggplot2 [@rGgplot2], Readr [@rReadr], Here [@rHere], Janitor [@rJanitor], KableExtra [@rKableExtra], Knitr [@rKnitr].

In the next section, we will discuss data including data source, methodology and features. After that, we will create a reproduction of the selected results to verify their data and their findings based on the data. In the last section, we will discuss our findings, including …. We will also conclude potential bias and weaknesses, as well as a push for future research

>>>>

---
title: "Misperceived Social Norms about Women Working Outside the Home and Its Effect on Women in Saudi Arabia"
author: 
  - Boxuan Yi
  - Ruoxian Wu
thanks: "Code and data are available at: https://github.com/ScarletWu/Misperceived-Social-Norms-Women-Working-Outside-the-Home-in-Saudi-Arabia. Replication on Social Science Reproduction platform is available at: https://www.socialsciencereproduction.org/reproductions/1557/"
date: "February 12, 2024"
date-format: long
abstract: "Husbands who hold guardianship and discourage their wives from working outside the home are often perceived as the main reason for the low female workforce participation in Saudi Arabia. Bursztyn, González, and Yanagizawa-Drott explore this social norm through surveys, experiments and visualizations, revealing that a majority of young husbands in Saudi Arabia privately support women working outside the home but underestimate the support of other men, and correcting this misperception increases husbands’ willingness to help wives search for jobs. This paper replicates the data from their study to analyze young husbands’ actual opinions and perceptions, confirming similar findings. This paper also discusses strategies for reducing misperceptions and the unusual Saudi female employment rate during the pandemic."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

Our paper will follow a reproduction of Leonardo Bursztyn, Alessandra L. González, and David Yanagizawa-Drott’s findings. We seek to replicate two claims, (1) There is a wedge between the actual and perceived proportion of men supporting women working outside the home, and (2) Most Saudi men who privately support WWOH fail to understand that others do as well, and they are more likely to help their wives find jobs when they know the actual portion of men supporting WWOH. The experiments and surveys results we will try to replicate are (1) the actual portion of support of WWOH from young husbands, (2) the existence of misperception, and (3) the effects of correcting beliefs on female employment in Saudi Arabia. Our reproduction used the programming language R [@r], the analysis used the following packages: Haven[@rHaven], Dplyr [@rDplyr], Ggplot2 [@rGgplot2], Readr [@rReadr], Here [@rHere], Janitor [@rJanitor], KableExtra [@rKableExtra], Knitr [@rKnitr].

In the next section, we will discuss data including data source, methodology and features. After that, we will create a reproduction of the selected results to verify their data and their findings based on the data. In the last section, we will discuss the impact of informational intervention, the use of social proof to overcome harmful norms, and the inverse pattern of female labor force participation rate in Saudi Arabia during the pandemic. We will also conclude ethics, potential bias, and weaknesses topics, as well as a push for future research.
